# `dplyr`

## `case_when()`

`dplyr::case_when` goes really well with `geom_text` (or `ggrepel`) for when you want to programmatically label a few of the most interesting features in your plots! And the criteria can be as complex as you want.

```{r case_when}
set.seed(10)
mydata <- 
  data.frame(
    x = 1:10,
    y = rnorm(10),
    name = c("Apple", "Banana", "Kiwi", "Orange", "Watermelon", "Grapes", 
             "Pear", "Cantelope", "Tomato", "Satsuma"),
    stringsAsFactors = FALSE
  ) %>% 
  mutate(
    name_poor = case_when(
      y < 0 ~ name,
      TRUE ~ ""
    )
  )

ggplot(mydata, aes(x = x, y = y)) + 
  geom_point(size = 5) + 
  geom_text_repel(aes(label = name_poor), point.padding = 2)
```

Credit: [\@rensa_co](https://twitter.com/rensa_co/status/976340414016843776?ref_src=twsrc%5Etfw)

## `mutate_at()`

`mutate_at()` takes a range of consecutive columns, with `var(col1:coln)` if you want to batch convert a bunch of columns:

```{r mutate_at}
iris %>% 
  mutate_at(vars(Sepal.Length:Petal.Width), as.character) %>% 
  as_tibble()
```

Credit: [\@vsbuffalo](https://twitter.com/vsbuffalo/status/831651327411302404?ref_src=twsrc%5Etfw)

## `mutate_if()`

Convert all factor columns to characters. 

```{r mutate_if}
iris %>% 
  mutate_if(is.factor, as.character) %>% 
  as_tibble()
```

Credit: [\@GojThomson](https://twitter.com/GojThomson/status/847241896015441921?ref_src=twsrc%5Etfw)

## `summarise_at()`

`dplyr::summarise_at()` applies multiple summary functions to multiple variables!

```{r summarise_at}
mtcars %>% 
  group_by(cyl, am) %>% 
  summarize_at(vars(disp, hp, mpg), funs(mean, sd))
```

Credit: [\@thomas_mock](https://twitter.com/thomas_mock/status/967467213623119873?ref_src=twsrc%5Etfw)
